---
title: "R Programs"
Date: 4 Feb 2023
Name: K Lalith Aditya
Regd No: 22231
Class: Msc 1st Year
Semester: 2
output: html_notebook
---

## Vectors

```{r}
abd<-c("hello","world")
print(abd)
```

### concatenating two vectors

```{r}
xa<-c('sai')
xb<-c('ram')
cat(xa,xb)
```

### Operations on vectors

```{r}
#adding corresponding elements in two vectors
a<-c(1,2,3)
b<-c(4,5,6)
c<-a+b
print(c)
```

class

```{r}
#class of c 
print(class(c))
```

Multiplication

```{r}
#multiplying corresponding elements in two vectors
a<-c(1,2,3)
b<-c(4,5,6)
c<-a*b
c
```

Subtraction

```{r}
#subtracting corresponding elements in two vectors
a<-c(1,2,3)
b<-c(4,5,6)
c<-a-b
c
```

Division

```{r}
#dividing corresponding elements in two vectors
a<-c(1,2,3)
b<-c(4,5,6)
c<-a/b
c
```

## Lists

```{r}
mysub<-list(c("regression","multivariate","machine learning","big data","data engineering"))
print(mysub)
print(class(mysub))
```

Appending two lists

```{r}
a<-list(1,2,3)
b<-list(5,6,7)
z<-append(a,b)
z
```

## Matrices

```{r}
#Creating a Matrix of class seating
bench<-matrix(c('aditya','kumar reddy','satya sai','vamsee','hemanth','lalith','pavan','mathura','saideva','varanasi','aharneish','anirudh','srihari','swaroop'),nrow=2,ncol = 7,byrow=TRUE)
print(bench)
```

Taking by row = False or default taking as by column

```{r}
bench<-matrix(c('aditya','kumar reddy','satya sai','vamsee','hemanth','lalith','pavan','mathura','saideva','varanasi','aharneish','anirudh','srihari','swaroop'),nrow=2,ncol = 7,byrow = FALSE)
print(bench)
```

## Arrays

```{r}
#printing array elements
a <- array(c("o","x"),dim=c(1,2))
i<-0

while(i<=5){
  print(a)
  i<-i+1
}


```

## Factors

```{r}
#Taking Cars types

cars<-c('tata','suzuki','maruti','suzuki','tata','benz','toyota')
factor_cars<- factor(cars)

print(factor_cars)
print("   ")
print(class(factor_cars))

print(nlevels(factor_cars))
```

## DataFrames

```{r}
sports_perf<-data.frame(
  name=c('aditya','kumar','satya','vamsee','hemanth'),
  height_cm=c(170,169,175,169.5,173),
  weight_kg=c(75,89,66,89,77),
  age_yrs=c(22,21,22,21,22),
  hund_mtr_sec=c(12,9,10,14,13),
  four_hundr_sec=c(40,37,42,39,36)
)
print(sports_perf)
```

To know what all variables are present

```{r}
ls()
```

Deleting Variables

```{r}
print("Before Deleting:")
new_var<-'I am new Variable'
ls()
print("After Deleting:")
rm(new_var)
ls()



```

In the above code the variable new_var got deleted

## Basic Arithmetic Operations 

```{r}
a<-2
b<-3


sprintf("Add:- %d",a+b)
sprintf("sub:- %d",a-b)
sprintf("mul:- %d",a*b)
sprintf("div:- %f",b/a)
sprintf("power:- %d",a^b)
sprintf("modulus:- %d",a%%b)
sprintf("Integer Division:- %d",a%/%b)
```

## Comparison Operations

Equality condition

```{r}
a<-6
b<-6
if(a==b){
  print("both variables are equal")
}else{
  print("both variables are not equal")
}
  
```

Not Equal

```{r}
a<-7
b<-6
if(a!=b){
  print("both variables are not equal")
}else{
  print("both variables are equal")
}
```

```{r}
a<-6
b<-7
if(a>=6){
  print(a)
}
if(a<b){
  print("b is less than a")
}
if(b>=7){
  print(TRUE)
}
```
