---
output:
  html_document: default
  pdf_document: default
---
## Title: "R Programs"
## Date: 8 Feb 2023
## Name: K Lalith Aditya
## Class: Msc 1st Year
## Semester: 2
## Regd No: 22231


```{r}
# Add two vectors

v <- c( .2,905.5,996) 
t <- c(87, 30, 409)
print(v+t)
```
Multiply two vectors
```{r}
p<- c(24,25.56,26)
q<- c(38,47,64)
print(p*q)
```

Subtract 2nd vector from the first
```{r}
v <- c(1.2,85.5,5.6,45) 
t <- c(.8, 7.3, 3.4,99)
print(v-t)

```
Divide the first vector with the 2nd vector
```{r}
p<-c(18,51.51,7,6)
q<-c(18,31,41,5)
print(p/q)
```
Remainder of the first vector with the second 
```{r}
v <- c( 12,15.5,26,61) 
w<- c(8.99, 3.56, 4.999,34)
print(v%%w)  

```
Division of first vector with the second
```{r}
v <- c(12,57,6.87,1)
w<- c(81, 3.99, 4.98,90) 
print(v%/%w)
```
Colon operator:
```{r}
s <- 1:16 
print(s)

```

%in% operator:
This is used to identify an element in the vector

```{r}
a<-5
b<-11
list<-1:10
if(a %in% list){
print("a is present in the list")
}else
{
print("a is not present in the list")
}
if(b %in% list){
print("b is present in the list")
}else
{
print("b is not present in the list")
}
```
%*%   This operator is used to multiply a matrix
```{r}
M = matrix(c(2,0,2,0),nrow = 2,ncol = 2,byrow = TRUE)
Msquare = M%*%M
print(Msquare)
```
# Control Structures
if statement
```{r}
z<- -1L
if(is.integer(z)){
  print("Yes z is an integer")
}
```
if,else if, else statements
```{r}
z<-"str"
if(typeof(z)==typeof("lol"))
{
  print("z is a character")
}else if(typeof(z)==typeof(3))
{
  print("z is an integer")
}else{
  print("z is neither an integer nor a character")
}
```

# Loops
while loops
```{r}
a<-10
while(a>=1){
  print(a)
  a<-a-1
}
```
Repeat Loop
```{r}
count<-0
repeat{
  count<-count+1
  if(count==10){
    print("count is 10")
    break
  }
}
```
R For Loop
```{r}
x<- 10:12
for(v in x){
  print(v)
}
```
```{r}
v <- letters[1:4]
print(v)
for(z in v)
{ 
  print(z) 
}

```
next and break statement

```{r}
elements<-list("a","b","c","d","e","f")
for(i in elements){
  if(i == "b"){
    next
  }
  if(i == "f"){
    break
  }
  print(i)
}
```

```{r}
mtcars
head(mtcars)

```
scatter plot mpg(mileage) Vs hp(horse power)
```{r}
plot(mtcars$mpg, mtcars$hp,
     col='violet',
     main='Scatterplot',
     xlab='mpg',
     ylab='hp',
     pch=20)
abline(lm(mtcars$hp ~ mtcars$mpg, data = mtcars), col = "blue")
```
```{r}
corr<-cor(mtcars$mpg, mtcars$hp)
sprintf("The co-relation between the features is %f",corr)
```
